\Title

### 2020-03-03 manuscript/manuscript.tex
Reformat ground survey parameter table
Replace full list of parameters for ranges when possible.
Change table design to better fit paper width and visualization.

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \GroundSourceBellowDataConstantDepthDepth
                   & \GroundBlockMedianSourcesConstantDepthDepth
                   & \GroundGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesConstantDepthSpacing
                     & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBellowDataRelativeDepthDepth
                   & \GroundBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \GroundSourceBellowDataVariableDepthDepth
                   & \GroundBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBellowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \GroundBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{booktabs}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Interval}} \\
        \hline

        \multirow{5}{*}{Source Bellow Data}
            & Constant Depth
                & Depth (km)
                & \GroundSourceBellowDataConstantDepthDepth
                & \GroundSourceBellowDataConstantDepthDepthInterval \\
            \cline{2-5}
            & Relative Depth
                & Depth (km)
                & \GroundSourceBellowDataRelativeDepthDepth
                & \GroundSourceBellowDataRelativeDepthDepthInterval \\
            \cline{2-5}
            & \multirow{3}{*}{Variable Depth}
                & Depth (km)
                & \GroundSourceBellowDataVariableDepthDepth
                & \GroundSourceBellowDataVariableDepthDepthInterval \\
            &
                & Depth factor
                & \GroundSourceBellowDataVariableDepthDepthFactor
                & \GroundSourceBellowDataVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \GroundSourceBellowDataVariableDepthKNearest
                & \GroundSourceBellowDataVariableDepthKNearestInterval \\
        \hline

        \multirow{8}{*}{Block median sources}
            & \multirow{2}{*}{Constant Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesConstantDepthDepth
                & \GroundBlockMedianSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundBlockMedianSourcesConstantDepthSpacingInterval \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesRelativeDepthDepth
                & \GroundBlockMedianSourcesRelativeDepthDepthInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \GroundBlockMedianSourcesRelativeDepthSpacingInterval \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (km)
                & \GroundBlockMedianSourcesVariableDepthDepth
                & \GroundBlockMedianSourcesVariableDepthDepthInterval \\
            &
                & Depth factor
                & \GroundBlockMedianSourcesVariableDepthDepthFactor
                & \GroundBlockMedianSourcesVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \GroundBlockMedianSourcesVariableDepthKNearest
                & \GroundBlockMedianSourcesVariableDepthKNearestInterval \\
            &
                & Spacing (km)
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \GroundBlockMedianSourcesVariableDepthSpacingInterval \\
        \hline

        \multirow{3}{*}{Grid Sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (km)
                    & \GroundGridSourcesConstantDepthDepth
                    & \GroundGridSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                    & \GroundGridSourcesConstantDepthSpacing
                    & \GroundGridSourcesConstantDepthSpacingInterval \\
            &
                & Pad
                    & \GroundGridSourcesConstantDepthPad
                    & \GroundGridSourcesConstantDepthPadInterval \\
    \end{tabular}
\end{table*}
